Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-05 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
fix figure 5, add refs

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log (average area)') +
  xlab('Age in days') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)
```

```{r}
# eye distance dataframe
eye_dist <- all_vid_data %>%
  group_by(child_id, age_day_bin) %>%
  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_faces = sum(num_faces)) %>%
  filter(num_faces>2000) %>%
  mutate(variable = 'Eye distance')
```

@@

We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development. We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015]. 
Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2017see; @fausey2016]. 
As children explore the world on their own [@xu2019towards], they may experience fewer close-up interactions with their caregivers and more bouts of play where they are exploring the objects in their environment.

>>>>

ggplot(avg_area_by_age, aes(x=age_day_bin, y=log(avg_area), col=child_id, size=num_detect)) +
  geom_point(alpha=.1) +
  facet_grid(~label) +
  geom_smooth(method='lm') + 
  ylab('Log area (average proportion of frame)') +
  xlab('Age (in months)') +
  scale_color_brewer(palette="Dark2", name = "Child") +
  guides(size = FALSE)
```

```{r}
# eye distance data frame
eye_dist <- all_vid_data %>%
  group_by(child_id, age_day_bin) %>%
  summarize(eye_distance = mean(avg_eye_distance, na.rm=TRUE), num_faces = sum(num_faces)) %>%
  filter(num_faces>2000) %>%
  mutate(variable = 'Eye distance')
```

@@

We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development. We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions, in keeping with prior work examining the sizes of faces in the infant view during the first year of life [@Jayaraman2015; @sugden2017hey; @sugden2014spy; @sugden2019these]. 
Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent [@franchak2017see; @fausey2016]. 
As children explore the world on their own [@xu2019towards], they may experience fewer close-up interactions with their caregivers and more bouts of play where they are exploring the objects in their environment.
